\documentclass[a4paper,14pt]{article}
\usepackage{graphicx}
\begin{document}
\begin{center}
\Huge\textbf{User Manual}
\\[0.2in]
\huge\textbf{NETWORK SIMULATION and GRAPH ANALYSIS}
\\[0.2in]
\large\textbf{BY}
\\[0.2in]
\Large\textbf{Nishant Kumar}
\\
\Large\textbf{V.A.V.S. Nikhil}
\\
\Large\textbf{Mohit Agarwal}
\\[10in]
\huge\textbf{CONTENTS}
\\[0.4in]
\end{center}
\begin{flushleft}
A. \large\textbf{Instructions for executing}\\
\begin{enumerate}
\item There are two folders 1)NetworkGen 2)Analyser
\item To run the first part i.e. NetworkGen
\begin{enumerate}
\item Open terminal.
\item cd to NetworkGen
\item Type "make" and wait for code to compile.
\item Type "./run.sh -d (day) (inp)", where day-> No. of days for which you want to run the simulation and inp-> name of input file to clean.
\item Type "make clean". 
\end{enumerate}
\item To run the first part i.e. NetworkGen
\begin{enumerate}
\item Open terminal.
\item cd to Abnalyser
\item Type "make" and wait for code to compile.
\item Type "./run.sh "
\item Type Press 'q' for exit.
\item Type "make clean". 
\end{enumerate}
\item If in the second part user exits without pressing q, message ques won't be deleted and type "./bash\_file.sh" 
\end{enumerate}
B.	 \large\textbf{System Requirements}\\
 Since message queues used by us only work on a unix system. Hence our system requirement is unix/linux for sure.
\\[0.1in]C.\large\textbf{Queries supported}\\
\begin{enumerate}
\item The clique of a node.
\item The length of shortest path between two nodes.
\item List of people on the shortest path of two nodes.
\item Largest short path in the graph.
\item Importance of the given node.
\item For checking if there is more important friend of a node than itself.
\end{enumerate}
D.\large\textbf{Format of entering the nodes}\\
First specify the university as it was given in the graph and then specify the type and number.
i.e. To specify a person with node id IITD\_f\_180 You have to do IITD f180.

\end{flushleft}
\end{document}